%gram = xelatex
\input{prekux.tex}

\bibliography{cite}

%\includeonly{analysis}

\begin{document}
\begin{english}
\include{front}

\include{theory}

\include{sim}

\include{experiment}

\include{data}

\include{analysis}

\chapter{Conclusion}
In this thesis, we attempted to estimate the effect of a $qq\rightarrow\gamma\gamma$ contact interaction, with associated energy scale $\Lambda$, upon the distribution of $M_{\gamma\gamma}$ in diphoton events produced in proton--proton collisions at the LHC.

The new interaction was introduced in a modified Standard Model through the effective Lagrangian approach.

This is a highly non--trivial endeavour, as there are no suitable \atlas{} Monte Carlo sets on which to base this attempt. We found that even the Monte Carlo set created to simulate the Standard Model $qq\rightarrow\gamma\gamma$ process did not satisfactorily cover the sensitive region at high invariant masses. Thus, we were required to go through every step needed to create a suitable MC data set. This process involved long processing times, using large and cumbersome software packages. In the end, there is room for improvement in the outcome of this process.

We exploited the quadratic form of the expression for the strength of the new interaction to derive a shape for the distribution of events at arbitrary $\Lambda$ from distributions created at two discrete values of $\Lambda$ and the Standard Model distribution. This involved describing the shape of the distribution by performing a simultaneous fit over all three distributions.

A data driven background estimation technique was applied to data taken from the \atlas{} detector at the LHC. The resulting estimated background distribution was combined with appropriate distributions from Monte Carlo, and its shape was extrapolated into the sensitive invariant mass region above 1\,000 GeV.

A most likely value of $\Lambda$, with accompanying confidence interval was found by comparing the data distribution of invariant mass, $M_{\gamma\gamma}$, with the Monte Carlo distribution, combined with appropriate backgrounds, using a maximum profile likelihood procedure, which took systematic uncertainties into account. The invariant mass was chosen as the discriminating variable among several other variables, for its discriminating power and robustness.

The profile likelihood fit give as a result a 95\% confidence interval for $\Lambda$ between 763 and 900 GeV. This result is influenced by the poor statistics and high uncertainty in the signal region of the \atlas{} $\gamma$jet Monte Carlo sample. The result could be improved if a sample with better statistics were available. We have also pointed a direction for better accounting for the uncertainty associated with this sample in the context of a likelihood profile fit.

The analysis already included methods that produced errors for bins individually, rather than assuming correlation across all bins. This process is easily extended to accept per--bin or per--event uncertainties for detector effects or Monte Carlo uncertainties. It can also be extended to account for correlated errors.

Lastly, an analysis similar to this one on the data from 13 TeV collisions being taken at the LHC this year (2015) would of course have substantially better sensitivity due to the strong enhancement with energy.

\section{Addendum}
An additional estimate for the confidence limits on $\Lambda$ became available before the thesis defence. A profile likelihood fit which included uncertainties on the background distribution finds a confidence interval for $\Lambda$ which agrees with the Standard Model, and sets a lower limit on $\Lambda$ of 779 GeV.

\printbibliography[title=References]

\include{appendix}

\phantom{.}

\thispagestyle{empty}
\vspace{\fill}
\begin{center}
This is version 2 of the thesis, which contains minor corrections and additional results which became available before the thesis defence on 30 october 2015.
\end{center}

\end{english}
\end{document}
