...additive under Lorenz boosts.

Of the three detector types, the most important to the search for photons is the electromagnetic calorimeter.

The muon tracker forms the outermost, and largest, part of the detector, since muons are one of only a small number of particles that can be expected to penetrate through the calorimeter layer regularly. Neutrinos will do so as well, however, capturing neutrinos with \textsc{atlas}' mere 90~000~t of material and 7~000 m$^3$ detector volume \cite{atlasweb} is something of a lost cause. Like the inner detector, the muon detector localises the track of a passing charged particle by picking up the ionisation trail it leaves in a sensitive material. Also like the inner detector, it ascertains the momentum and charge of passing charged particles by measuring their deflection by an applied magnetic field.

The inner detector uses two distinct detector technologies to localise the tracks of charged particles that pass through it. The innermost layer uses silicon semiconductor chips to detect the charge left in a track in a compact, high-precision system. The outer part of the inner detector uses drift straws---which pick up the ionisation charge left in an inert gas by attracting it to a high-voltage wire in the centre of the straw---to more economically, in terms of material, readout complexity and, well, economy, cover a larger volume.

Both the straw detector and part of the silicon detector, the strip detector, are very long structures, which can only report that a hit has occurred somewhere along its length. To compensate for this, successive layers of detector elements are placed at an angle to one another. The innermost layer of the silicon detector, the pixel detector, is also segmented lengthwise, and so does not require this. Still, the detector only provides a list of detector elements that have registered a hit. Particle tracks are fitted to these hits in one of the stages of the subsequent analysis of an event.

There are two calorimeter systems in \textsc{atlas}. Both are supposed to stop the particles that pass through them, and measure the energy that they deposit. \textsc{Atlas} only uses sampling calorimeters, meaning that the absorbing material has sensitive layers inserted into it at intervals. These sensitive layers measure how deep into the absorbing material the particles penetrate, and thus how much energy the carried before entering the calorimeter. In the barrel section of the hadronic calorimeter---the outermost half of the calorimeter system, which is supposed to catch the, by assumption, hadronic events that penetrate the electromagnetic calorimeter, the inner half of the calorimeter system---the sensitive layers are scintillators, a material that luminesces when exposed to ionising radiation, and the absorbing layers are iron. The remaining calorimeters, which covers both the EM calorimeters and the endcap hadronic calorimeters, have both iron and lead as absorbing material, and liquid argon as the sensitive material. As with the straw detectors, activity in the liquid argon layers are detected by an electrode, which picks up the ionisation charge left in the argon.

[for safe keeping:]

The level-1 trigger, which must perform selection at the same cadence as the collision events occur, runs on specialised hardware built into the calorimeter and muon systems, and evaluates the worthiness of an event based solely on the information available to them locally. As an example, the level-1 trigger used to select data for this thesis, called \texttt{2g40\_loose}, requires that the EM calorimeter has recorded at least two deposits of 40 GeV transverse energy, which fulfils the loose shower shape cuts. These hardware triggers reduce the event frequency from 20 MHz to 100 kHz.

The level-2 trigger has access to full precision data from all parts of the detector, and runs on a dedicated computing cluster close to the detector. It combines information from all parts of the detector to better determine if the deposits identified by the level-1 trigger are actually interesting events. Staying with photon candidates in the EM calorimeter, this trigger might use information from the hadronic calorimeter to separate out hadronic jets, or tracking information from the inner detector to distinguish between neutral and charged particles. This trigger reduces the data rate to below 10 kHz.

The level-3 trigger---or the event filter---looks at fully reconstructed events and calculated and derived physical properties, such as transverse momentum, which allows it to cut in those quantities to further refine the event selection. This trigger brings the data rate down to the final rate of around 300 Hz on average. The output rate varies, since the rates with which interesting events occur are purely random, and the final data rate can peak up to 600 Hz for short periods.